From Classification to Naming:\\ Modeling Entry-level Names for Objects in Images

### 2020-01-10 papers/ACL2020/analysis.tex
merges changes by CS and GBT--not submitted version

The previous section looked at the performance of the different naming models using a standard single-label evaluation scheme.
%vanilla evaluation methods like accuracy.
This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
In the following, we use our verification data to assess the severity of errors in different naming models.

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples).
Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a wrong name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}

\begin{tabularx}{.46\textwidth}{@{~}lX}
	\textbf{\sameobject:} & alternative name for the same object, estimated from \mn and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
%(see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
	\textbf{LowCount:} & name produced by 1 annotator\\
	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt}; also estimated from WordNet)\\
\end{tabularx}

@@

Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (viz.\ less) than 90\% of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\

>>>>

The previous section looked at the effectiveness of the different naming models using a standard single-label evaluation scheme.
%vanilla evaluation methods like accuracy.
This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
In the following, we use our verification data to assess the severity of errors in different naming models.

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples).
Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name)
%wrong name), % [CS] we did not do an exhaustive collection of object names, so the name may still be correct, but just very rare for the instance
 we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}

\begin{tabularx}{.47\textwidth}{@{~}lX}
	\textbf{\sameobject:} & alternative name for the same object, as estimated from its valid \mn names (see Section~\ref{sect:mn_verification}), or a WordNet synonym or hypernym of the valid MN names (\name{house/building}; \citealt{fellbaum1998wordnet})\\
	%and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
%(see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
	\textbf{LowCount:} & name produced by 1 annotator\\
	\textbf{Related:}& a WordNet hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\
\end{tabularx}

@@

Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (vs.\ less) than~$90\%$ of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\

### 2020-01-10 papers/ACL2020/introduction.tex
merges changes by CS and GBT--not submitted version

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal}, etc.). 
The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~(e.g.,~\citealt{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to predict \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, left image).
%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe here.%
\footnote{Data and code for this paper will be made available upon publication.}
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences (frequencies) for instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}

In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others are much more specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

@@

Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}. 
More precisely we define entry-level name as follows:\\
%, \mn enables us to define entry-level name as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

>>>>

Objects, being members of many \categories, can be called by many names (e.g.,~a duck can be called \name{duck, bird, animal}, etc.). 
The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~(e.g.,~\citealt{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to predict \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, left image).
%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data which we also describe here.%
\footnote{Data and code for this paper will be made available upon publication.}
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences (frequencies) for instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}

In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs. slightly pointed). 
But it raises the issue of whether these models could be directly used for more human-like object naming.
% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.

@@

Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}. 
%More precisely w
We define entry-level name as follows:\\
%, \mn enables us to define entry-level name as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

### 2020-01-10 papers/ACL2020/manynames.tex
merges changes by CS and GBT--not submitted version

We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn.
Since the task was multiple-choice we could conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
We ran all the \mn data (response sets) through our verification, with two exceptions: 
response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
Each of the remaining $19,427$ images, with the target object highlighted with a bounding box, were presented to $3$~annotators, with a list of all its names to be verified (Figure~1 in supplementary material; on average $4$ names per object).
They were asked to judge the adequacy\footnote{
	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
} of each name among ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (encoded below as 1.0, 0.5 and 0.0, respectively).
If they did not select ``adequate'' they had to specify the type of inadequacy from ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
Lastly, annotators had to judge which names were likely intended for the same object, through an interface where they would assign the same color to names intended for the same object.
%% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
Overall, $255$~participants annotated $69,356$~object-name pairs (each pair receiving 3 annotations).

@@

\paragraph{Judgment Aggregation}
We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority.
%% SHORTENING %%  (counting ``none'' for annotators saying there is no inadequacy). 
Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
This is high given the complexity of the task
%% SHORTENING %% , essentially mind-reading what the original \mn annotators may have meant, 
and the fact that pictures and bounding boxes are sometimes unclear.
Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types.
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
	\caption{Verification results: a. counting individual annotations; b. counting image-name pairs with their aggregated scores. Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

We aggregate the judgments of whether two names were intended for the same object in two ways, for different purposes: \sameobject and \cluster.
% \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it? In this case, it would be "aggregating name cluster", no?! So what you did for the first aggregation (modeling) was a pair-wise aggregation?} \mw{I don't understand this...}
First, for analysing computational object naming models (Section~\ref{sec:analysis}), 
% we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 	% <- Carina's reformulation, but not strictly true and not clear to me.
we want to know primarily whether the name predicted by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name.
This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, and for that we need to do clustering (the pairwise majority rule does not result in a proper clustering). 
We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (hence all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis). The alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters), would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.
}

@@

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
This predicts that we will find a stable ordering of entry-level names. 
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name (covering 281 of the 442 entry-level names of \mn).
These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, there is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).

>>>>

We recruited annotators from Amazon Mechanical Turk\footnote{
	\url{https://mturk.com}
} (AMT) to categorize the object-name pairs from \mn.
Since the task was multiple-choice we could conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
We ran all the \mn data (response sets) through our verification, with two exceptions: 
response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
Each of the remaining $19,427$~images, with the target object highlighted with a bounding box, were presented to $3$~annotators, with a list of all its names to be verified (Figure~1 in supplementary material; on average $4$~names per object).
They were asked to judge the adequacy\footnote{
	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
} of each name among ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (encoded below as 1.0, 0.5 and 0.0, respectively).
If they did not select ``adequate'' they had to specify the type of inadequacy from ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
Lastly, annotators had to judge which names were likely intended for the same object, through an interface where they would assign the same color to names intended for the same object.
%% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
Overall, $255$~participants annotated $69,356$~object-name pairs (each pair receiving 3 annotations).

@@

\paragraph{Judgment Aggregation}
We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority.
%% SHORTENING %%  (counting ``none'' for annotators saying there is no inadequacy). 
Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is~$0.80$ (\mbox{std=$0.093$}).
The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is~$86\%$, and agreeing on whether two names were intended for the same object is~$94\%$.
This is high given the complexity of the task
%% SHORTENING %% , essentially mind-reading what the original \mn annotators may have meant, 
and the fact that pictures and bounding boxes are sometimes unclear.
Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types.
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
	\caption{Verification results: a. counting individual annotations; b. counting image-name pairs with their aggregated scores. Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

We aggregate the judgments of whether two names were intended for the same object in two ways, for different purposes: \sameobject and \cluster.
% \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it? In this case, it would be "aggregating name cluster", no?! So what you did for the first aggregation (modeling) was a pair-wise aggregation?} \mw{I don't understand this...}
First, for analysing computational object naming models (Section~\ref{sec:analysis}), 
% we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 	% <- Carina's reformulation, but not strictly true and not clear to me.
we want to know primarily whether the name predicted by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name.
This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, which requires clustering (the pairwise majority rule does not result in a proper clustering). 
We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of~$.5$, using as distance between two names the proportion of annotators saying they do not name the same object (hence all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis). The alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters), would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.
}

@@

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
This predicts that we will find a stable ordering of entry-level names. 
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name (covering $281$~of the $442$~entry-level names of \mn).
These names, which are a clear winner at least once, are so still on average only in $46\%$~of cases where there is a clear winner at all (meaning in the other $54\%$~of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, there is still a clear winner only in $66\%$~of cases where there is one (std\mbox{$=.35$}, skewed with about half over $80\%$).
